---
output: github_document 
title: "Quickly Adding Dummies to Event Studies"
---

```{r setup, include=FALSE,echo = FALSE}
knitr::opts_knit$set(base.dir = "~/gannawag.github.io/docs/", base.url = "/")
knitr::opts_chunk$set(fig.path = "assets/")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = FALSE)

```



A problem I am faced with sometimes is to run a regression with a set of event-time dummy variables as regressors. The norm is to use event time -1 as the omitted category so the coefficients show the "effect" of the treatment in `\tau` periods since the event. 

It turns out you can do the creation and inclusion in a regression of these event time dummies pretty easily in R. 

First, use the `fastDummies` package to create the dummies and "merge" them back on to the original data. The key function is `dummy_cols` which takes in a column that we want to turn into the dummies. So if the column is "event_time" then we will end up with a set of dummy variables for each value of event time. The other arguments to `dummy_cols` are a `select_columns` list and an instruction to remove the selected columns from the result.
```{r, eval=F}
#install.packages("fastDummies") #run if package not installed
dt <- cbind(dt, #cbind so we can merge the dummies back to the original
            fastDummies::dummy_cols( 
              dt[,.(event_time)], #the column we want to turn into dummies
              select_columns = "event_time", #select this column
              remove_selected_columns = T)) #don't want to have duplicate names
```
Now that our data.table has a a bunch of new columns that are the dummy variables, we need to get them into a regression. 

The easiest way to do this is to get a new object that is just a vector of the dummy variables we just created, turn that vector into a formula, and then include the formula in the regression. The other key here is to get the names in the order of the event time, so when they go in the regression we don't get confused by the output ordering. To do that, add another vector for the order in which we want the names to appear.
```{r,eval=F}
#get formula for regression so we don't have to type it in when we add more weeks
names_dt <- data.table(names = names(dt)[grepl("event_time", names(dt))],
                        order = as.numeric(
                          gsub(".*?_","",names(dt)[grepl("event_time",names(dt))]))
                        )
setorder(names_dt, order)
```

Now include the names in the regression using the `as.formula()` function, with some use of the `collapse` feature in the `paste` function. Notice the use of `paste0` vs `paste`. If you want to include other variables in the regression, you can just insert them in the `paste0` as additional arguments. 
```{r,eval=F}
#this will show coefficients relative to omitted event time period
reg <- lm(
  as.formula(
    paste0("outcome ~ ", 
           paste(names_dt$names, collapse = " + ")
    )
  ),
  data = dt)

```
